---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# LinearModelAnalysis

<!-- badges: start -->
[![R-CMD-check](https://github.com/Mikafzx/LinearModelAnalysis/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/Mikafzx/LinearModelAnalysis/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/Mikafzx/LinearModelAnalysis/branch/main/graph/badge.svg)](https://app.codecov.io/gh/Mikafzx/LinearModelAnalysis?branch=main)
<!-- badges: end -->

The goal of LinearModelAnalysis is to reproduce the result of lm() and summary(), output the residuals, fitted_values, df, coeff_table（which include Estimates, Std.Error, t value and p value), R_squared, adj_R_squared, F_statistic, p-value of F_test and CI_95  of the fitted model.

## Installation

You can install this package with the following code:

``` {r}
# install.packages("devtools")
devtools::install_github("Mikafzx/LinearModelAnalysis")
```

## Example

This is an example on how to use the package.

```{r example}
library(LinearModelAnalysis)
data(mtcars)
mlr_analysis(formula = mpg ~ hp + cyl, data = mtcars)
```


