---
title: "tutorial"
author: "Zhuoxin Fu"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(LinearModelAnalysis)
library(bench)
data("mtcars")
```

# Purpose of the package

This package include a r function mlr_analysis which take a multiple linear formula 
and the data set as input, fit the model and output the residuals, fitted_values, df, 
coeff_table（which include Estimates, Std.Error, t value and p value), R_squared,
adj_R_squared, F_statistic, p-value of F_test and CI_95  of the fitted model.

# Example using this package

Here is an example of fitting a model with three covariance from the dataset mtcars and its' model analysis.
```{r}
mymodel1 = mlr_analysis(formula = mpg ~ hp + cyl + wt, data = mtcars)
mymodel1
```
Here is an example of fitting a model with interaction from the dataset mtcars and its' model analysis.
```{r}
mymodel2 = mlr_analysis(formula = mpg ~ hp + cyl + wt + qsec + cyl * wt, data = mtcars)
mymodel2
```
# Benchmark between mlr_analysis and the original lm function
```{r}
# fit the model which contains interaction with original lm function
lm_model = lm(mpg ~ hp + cyl + wt + qsec + cyl * wt, data = mtcars)
sum_lm = summary(lm_model)
```

```{r}
# compare the coefficients between two functions
all.equal(as.numeric(mymodel2$coeff_table), as.numeric((sum_lm)$Coefficients))

# compare the residuals between two functions
all.equal(as.numeric(mymodel2$summary_table$residuals), as.numeric(lm_model$residuals))

# compare the fitted values between two functions
all.equal(as.numeric(mymodel2$fitted_values), as.numeric(lm_model$fitted.values))

# compare the df between two functions
all.equal(as.numeric(mymodel2$df), as.numeric(sum_lm$DF))

# compare the  between two functions
all.equal(as.numeric(mymodel2$R_squared), as.numeric(sum_lm$r.squared))

all.equal(as.numeric(mymodel2$F_stat), as.numeric(sum_lm$fstatistic))
```

```{r}

```
